Proposed Solution

### 2016-11-14 Ennan-Proposal/impact.tex
stuff

>>>>

Since her beginning of teaching at Yale, the PI is actively including topics from her 
research into her courses (such as ``Software Analysis and Verification''). This way
she motivates undergraduate student to get involved in the research. Until this day 
she supervised 29 undergraduate student projects. Two students (Reinking, Cai) 
who did an undergraduate research projects with her are now PhD students at 
UC Berkeley, and two more students are applying (Anklessaria, La) to graduate schools 
this year.
